---
title: "Analysis Report 2: NEON Mosquito Trap Data"
author: "Courtney Lopez"
date: "4/16/2018"
bibliography: references.bib
csl: ecology.csl
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Delete this placeholder text, and replace it with your introduction text. You should include background on the NEON project including proper citations (e.g. [@thorpe2016introduction]), the sets of sites you are comparing, and other relevent background information related to your specific hypotheses, including perhaps information on the mosquito sampling design [@hoekman2016design].


Because species *Aedes communis* has the trait of living in woodland pools, we should see it only in the spring season at terrestrial sites back east and not in the others.


# Methods

Describe where the data came from, including how they were collected in the field (information is in the pdf file in the data folder), some information about those sites and why you chose them, and how you are analyzing them (e.g. using R to visualize the results and the statistical tests you will use).

# Results

Add a number of code chunks in the Results section. These should read in, subset and plot the data as needed (no need to save any figures to pdf, since they will be put into the rendered document when you click 'knit'), and, for any hypotheses that you want to test, an appropriate statistical test. You should have at least 5 figures and/or tables in this section, which you use to test your hypotheses against the dataset. I've included some starter code to read in and merge the two datasets. You should build on this code for your own analyses.

```{r load-packages}
library("dplyr")
library("tidyr")
library("ggplot2")
library("readr")
```

```{r read-in-datasets}
# this is the information on each of the trapping locations and trapping events
mos_trapping <- read_csv("data/raw_data/mos_trapping.csv")

# this is the info about the taxonomic identity of mosquitos found in the traps
mos_expert <- read_csv("data/raw_data/mos_expertTaxonomistIDProcessed.csv")
```

```{r join-datasets}
# split the 'subsampleID' column into two new columns, including one called
# 'sampleID' that we can use to match to the other dataset
mos_expert <- mos_expert %>%
  separate(subsampleID,
           into = c("sampleID", "subsample_number"),
           sep = "\\.S\\.")

# join the two datasets together based on the shared 'sampleIS' column
mos_all <- mos_expert %>%
  full_join(mos_trapping, by = "sampleID", suffix = c(".taxa", ".sample"))
```

```{r filter-by-speciesA}
mos_communis <- mos_all %>%
  filter(scientificName == "Aedes communis") %>%
  group_by(siteID.sample) %>%
  tally() %>%
  arrange(desc(n))
```

```{r boxplot-communis}
ggplot(data = mos_communis,
       aes(x = siteID.sample, y = n)) +
  geom_boxplot() +
  ggtitle("Number of mosquitos of Aedes communis present at NEON sites") +
  geom_col(fill = "red")
```

**Show where these are located on a map!**

```{r filter-data-elevation}
mos_elevation <- mos_all %>%
  filter(scientificName == "Aedes communis") %>%
  group_by(siteID.sample, elevation) %>%
  tally() %>%
  arrange(desc(n))
```

```{r geompoint-elevation}
  ggplot(data = mos_elevation,
  aes(x = siteID.sample, y = elevation)) +
  geom_point() + (aes(color = elevation)) +
  ggtitle("Elevations of where Aedes communis is found")
```

```{r anova-1}
fit <- aov(siteID.sample ~ elevation, data = mos_elevation)
```

```{r filter-by-speciesB}
mos_canadensis <- mos_all %>%
  filter(scientificName == "Aedes canadensis") %>%
  group_by(siteID.sample) %>%
  tally() %>%
  arrange(desc(n))
```

```{r boxplot-canadensis}
ggplot(data = mos_canadensis,
       aes(x = siteID.sample, y = n)) +
  geom_boxplot() +
  ggtitle("Number of mosquitos of Aedes canadensis present at NEON sites") +
  geom_col(fill = "green")
```

**Show where these are located on the map**

# Discussion

Discuss the results you found in the context of what you know about the site/sites and the predominant types of vegatation in those locations. Think also about the community dynamics of the mammal community at each of the sites, in the context of what you know about different types of species interactions, food webs, trophic transfer, etc.

# Sources Cited

